Ceph Parallel File System Evaluation Report

### 2013-08-29 ceph-initial.tex
Clarify rados 8 client scaling number

\begin{figure}[!t]
\centering
\includegraphics[width=3in]{data/rados_osd}
\caption{RADOS scaling on number of OSDs}
\label{fig:osd-scale}
\end{figure}

\begin{figure}[!t]
\centering
\includegraphics[width=3in]{data/rados_server}
\caption{RADOS scaling on number of servers}
\label{fig:oss-scale}
\end{figure}

@@

In this test, we exercise OSD servers from one to four, driven by four hosts
each with four RADOS Bench process. Each additional OSD server
adds eleven more OSDs into play. We observe that Ceph exhibits linear scaling with
regard to number of servers as well, at least in the given set of servers.
However, the peak performance we are seeing is about the half of what are
expecting from the SFA10K (compare to the baseline block I/O perforamnce number
presented in Section~\ref{sec:block-io}).

>>>>

\begin{figure}[!t]
\centering
\includegraphics[width=3in]{data/rados_osd}
\caption{RADOS scaling on number of OSDs: single server single client}
\label{fig:osd-scale}
\end{figure}

@@

\begin{figure}[!t]
\centering
\includegraphics[width=3in]{data/rados_server}
\caption{RADOS scaling on number of servers, with 8 clients}
\label{fig:oss-scale}
\end{figure}

In this test, we exercise OSD servers from one to four, driven by four hosts
each with four RADOS Bench process. Each additional OSD server adds eleven
more OSDs into play. The results are illustrated in
Figure~\ref{fig:oss-scale}. We notice that the read performance improved about
10% given eight clients instead of four, but write performance is mostly flat
for reason explained below. We also observe that Ceph exhibits linear scaling
with regard to number of servers, at least in the given number of servers.
However, the peak performance we are seeing is about the half of what are
expecting from the SFA10K (compare to the baseline block I/O performance
number presented in Section~\ref{sec:block-io}).
